%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Kimberly Heinemann - Resume
% 01/20/2017
%
% Reference:
% Debarghya Das (http://debarghyadas.com)


\documentclass[]{hieudo-build}
\usepackage{wasysym}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Rob 
Heinemann}
{\urlstyle{same}
	\phone \hspace{0.1mm} (845) 709-4576\\
	\faEnvelope {RobHeinemann1@gmail.com}\\
    \ {New York}\\
}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.37\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 

\subsection{Marist College}
\descript{Master's in Education}
\sectionsep
\subsection{University of Missouri}
\descript{B. of Journalism (print/digital news)}
B.A. in English (Creative Writing) \\
Minors: Business, Spanish\\
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
% \subsection{Programming}
\location{PC, Mac OS, Microsoft Office, Adobe InDesign CS4, Audacity, Soundslides, Dreamweaver, Flash, iPhoto, iMovie, Wordpress, Various CMS, podcasts, infographics computer-Assisted Reporting: analyze databases with Excel and Access.}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     AWARDS/ACTIVITIES
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards/Activities} 
• Honored with the Media/Arts Award from RCADD (Rockland Council on Alcoholism and other Drug Dependence, Inc). Was on RCADD board as media liaison\\
• Honored with Community Support Award from Boy Scouts Rockland District\\
• Revitalized the Nanuet Chamber of Commerce 2012. Currently on the executive board of the chamber\\
• On the steering committee of the Rebuild Highview Community Playground and several sub committees 2010 – 2011\\
• Graduated Latin Honors Cum Laude, Mark Twain Scholarship, Dean’s List\\
• IRE and MU’s National Institute for Computer-Assisted Reporting 2010 Boot Camp\\

%\sectionsep
%\DTMsetdatestyle{mylastupdate}
%\DTMdisplaydate{\the\year}{\the\month}{\the\day}{-1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{minipage} 
\hfill
\begin{minipage}[t]{0.62\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
\workplace{IntraFish Media}{Jan 2015–Present} \\
\position{Online Reporter}{Stamford, CT; Seattle, WA}
\vspace{0.9em} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Responsible for reporting, producing original daily content. Interviewed and develop relationships with variety of sources and executives.
\item Long-term investigative reporting and editing. Managed and reported on variety of court-related issues and lawsuits.
\item Prepare and send daily newsletter and breaking newsletter.
\item Travel domestically and abroad to represent Intrafish at various events and trade shows as well as report live from the events and expos.
\item Manage social media accounts, including Twitter, Facebook, LinkedIn, Instagram.
\item Take and edit podcasts, photos and videos. Video interview executives in the seafood industry. Coached the IntraFish team to do the same.
\end{tightemize}
\sectionsep

\workplace{AOL - Patch news}{July 2010-Jan 2014} \\
\position{Local Editor}{New York, New Jersey}
\begin{tightemize}
\item Held various roles including local editor of multiple Patch news sites in New York and New Jersey and was head of Rockland County Patch sites.
\item Responsible for reporting, producing original daily content, photos, video: breaking news, features, hard news, business, education, elections, government, arts and sports.
\item Manage and curate content on my local news sites and newsletters to increase Unique Visitor numbers.
\item Interact and engage with residential, business and government community to build an online presence.
\item Encourage user-generated content and community involvement, including recruiting a variety of contributors, such as bloggers; Monitored user-generated content.
\item Manage a budget and hire, train and assign a team of reporters, contract freelancers and photographers.
\item Be collaborative and constructive with all other company departments such as marketing, sales, editorial, etc.
\item Manage several social media sites.
\end{tightemize}
\sectionsep


\end{minipage} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\namesection{Kimberly Heinemann}
%{\urlstyle{same}
%	\phone \hspace{0.1mm} (845) 709-2348\\
%	\faEnvelope {KimberlyHeinemann73@gmail.com}\\
%}
    

\hfill


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Kimberly Heinemann}
{\urlstyle{same}
	\phone \hspace{0.1mm} (845) 709-2348\\
	\faEnvelope {KimberlyHeinemann73@gmail.com}\\
    \ {New York / Seattle}\\
}
    
    
\begin{minipage}[t]{1.0\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}


\workplace{Freelance Editor/Writer}{2014} \\
\position{}{New York, New Jersey}

\begin{tightemize} 
\item Freelanced for several projects such as the 2014 Jesse Kaplan Cookbook.
\end{tightemize}
\sectionsep

\workplace{Vox Magazine}{Aug 2009–May 2010} \\
\position{Contributing Writer}{Columbia, MO}
\begin{tightemize}
\item Traveled to an unfamiliar rural town for research.
\item Collected interviews as a compilation of a small town’s cultural identity.
\end{tightemize}
\sectionsep

\workplace{Columbia Missourian}{Jan 2009-May 2009} \\
\position{Multimedia and Web}{Columbia, MO}
\begin{tightemize} 
\item Collected and edited audio using Audacity; developed slideshow using Soundslides.
\item Took photos for web versions of articles and blogs.
\item Maintained an education blog for School House Talk.
\end{tightemize}
\sectionsep

\workplace{Columbia Missourian}{Jan 2009-May 2009} \\
\position{Copy Editor}{Columbia, MO}
\begin{tightemize} 
\item Edited print and web stories for spelling, grammar and AP style.
\item Designed newspaper layouts and wrote story headlines using InDesign.
\item Monitored and edited submitted blogs.
\end{tightemize}
\sectionsep

\workplace{Purple: Literary Magazine}{Jan 2006-May 2006} \\
\position{Staff Editor}{Columbia, MO}
\begin{tightemize} 
\item Reviewed and selected submitted works for publication.
\item Edited and designed pages using InDesign.
\end{tightemize}
\sectionsep

\workplace{Maneater}{Aug 2005-Dec 2005} \\
\position{Reporter}{Columbia, MO}
\begin{tightemize} 
\item Interviewed and wrote local stories such as alleged molestation charges against a teacher
\end{tightemize}
\sectionsep

\end{minipage}

\end{document}  
